Jaigo Technical Report

### 2007-12-19 paper/paper.tex
align on decimal points in tables

\tref{table:first50} shows the first 50 moves on a 19x19 board with human (black) versus crawler (white).
\begin{table}
  \rotatebox{90}{
    \begin{tabular}{ccccccccc} \toprule
      Function & Calls & Percent & Own Time (ms) & Time (ms) & Avg (ms) & Min (ms) & Max (ms) & File\\ \midrule
      (no name) & 109675 & 25.68 & 14310.594 &	36908.812 &	0.337 &	0.059	& 1593.542	& simple\_go.js (line 407)\\
      flood\_mark & 1618 & 14.17 & 7897.73 & 25481.245 & 15.749 & 0.162 & 1635.18 & simple\_go.js (line 807)\\
      (no name) &	194678 &	11.75	& 6551.626 &	6554.733 &	0.034 &	0.008 &	1555.243 &	simple\_go.js (line 819)\\
      string\_as\_move &	56065 &	7.48 &	4168.485 &	4169.549 &	0.074 &	0.011 &	1591.844 &	simple\_go.js (line 192)\\
      iterate	& 109676 &	7.19 &	4005.749 &	22595.463 &	0.206 &	0.011 &	1593.499 &	simple\_go.js (line 391)\\
      (no name) &	283642 &	4.9 &	2732.499 &	18589.343 &	0.066 &	0.015 &	1593.144 &	simple\_go.js (line 416)\\
      iterateOwnProperties &	5811	& 4.38	& 2440.378 &	2847.852 &	0.49 &	0.004 &	2.917 &	simple\_go.js (line 132)\\
      Set\_Goban &	2150 &	3.53 &	1968.651 &	1969.095 &	0.916 &	0.004 &	942.058 &	simple\_go.js (line 528)\\
      (no name) &	42734 &	2.99 &	1666.478 &	1666.716 &	0.039 &	0.008 &	935.83 &	simple\_go.js (line 835)\\
      update &	3662 &	2.9 &	1613.61 &	1614.099 &	0.441 &	0.004 &	1560.416 &	simple\_go.js (line 117)\\
      Add\_Block &	2340 &	2.8 &	1559.92 &	1560.774 &	0.667 &	0.007 &	1529.63 &	simple\_go.js (line 757)\\
      Calculate\_Neighbour &	448 &	2.67 &	1487.337 &	12205.939 &	27.245 &	0.019 &	1579.849 &	simple\_go.js (line 829)\\
      Simple\_Same\_Block &	2149 &	1.93 &	1073.573 &	8185.472 &	3.809 &	0.002 &	1556.376 &	simple\_go.js (line 606)\\
      List\_Block\_Liberties &	3210 &	1.56 &	871.609 &	5057.619 &	1.576 &	0.012 &	1593.058 &	simple\_go.js (line 863)\\ \bottomrule
  \end{tabular}}
  \caption{First 50 moves on a 19x19 board}
  \label{table:first50}
\end{table}

>>>>

\tref{table:first50} shows the first 50 moves on a 19x19 board with human (black) versus crawler (white).
\begin{table}
  \rotatebox{90}{%  fc%         own       time      avg       min       max file
    \begin{tabular}{lrD{.}{.}{2}D{.}{.}{3}D{.}{.}{3}D{.}{.}{3}D{.}{.}{3}D{.}{.}{3}l} \toprule
      Function & Calls & \multicolumn{1}{c}{Percent} & \multicolumn{1}{c}{Own Time (ms)} & \multicolumn{1}{c}{Time (ms)} & \multicolumn{1}{c}{Avg (ms)} & \multicolumn{1}{c}{Min (ms)} & \multicolumn{1}{c}{Max (ms)} & File\\ \midrule
      (no name) & 109675 & 25.68 & 14310.594 &	36908.812 &	0.337 &	0.059	& 1593.542	& simple\_go.js (line 407)\\
      flood\_mark & 1618 & 14.17 & 7897.73 & 25481.245 & 15.749 & 0.162 & 1635.18 & simple\_go.js (line 807)\\
      (no name) &	194678 &	11.75	& 6551.626 &	6554.733 &	0.034 &	0.008 &	1555.243 &	simple\_go.js (line 819)\\
      string\_as\_move &	56065 &	7.48 &	4168.485 &	4169.549 &	0.074 &	0.011 &	1591.844 &	simple\_go.js (line 192)\\
      iterate	& 109676 &	7.19 &	4005.749 &	22595.463 &	0.206 &	0.011 &	1593.499 &	simple\_go.js (line 391)\\
      (no name) &	283642 &	4.9 &	2732.499 &	18589.343 &	0.066 &	0.015 &	1593.144 &	simple\_go.js (line 416)\\
      iterateOwnProperties &	5811	& 4.38	& 2440.378 &	2847.852 &	0.49 &	0.004 &	2.917 &	simple\_go.js (line 132)\\
      Set\_Goban &	2150 &	3.53 &	1968.651 &	1969.095 &	0.916 &	0.004 &	942.058 &	simple\_go.js (line 528)\\
      (no name) &	42734 &	2.99 &	1666.478 &	1666.716 &	0.039 &	0.008 &	935.83 &	simple\_go.js (line 835)\\
      update &	3662 &	2.9 &	1613.61 &	1614.099 &	0.441 &	0.004 &	1560.416 &	simple\_go.js (line 117)\\
      Add\_Block &	2340 &	2.8 &	1559.92 &	1560.774 &	0.667 &	0.007 &	1529.63 &	simple\_go.js (line 757)\\
      Calculate\_Neighbour &	448 &	2.67 &	1487.337 &	12205.939 &	27.245 &	0.019 &	1579.849 &	simple\_go.js (line 829)\\
      Simple\_Same\_Block &	2149 &	1.93 &	1073.573 &	8185.472 &	3.809 &	0.002 &	1556.376 &	simple\_go.js (line 606)\\
      List\_Block\_Liberties &	3210 &	1.56 &	871.609 &	5057.619 &	1.576 &	0.012 &	1593.058 &	simple\_go.js (line 863)\\ \bottomrule
  \end{tabular}}
  \caption{First 50 moves on a 19x19 board}
  \label{table:first50}
\end{table}
